Boundary Labeling for annotated documents

### 2018-01-27 LaTeX/Paper.tex
Paper: Edited Fig. 1.1 to include the Routing Area; minor corrections. Program: No changes.

\begin{figure}%{r}{0.35\textwidth}
 \captionsetup{justification=centering, margin=0.75cm}
 \centering
  \includegraphics[scale=0.90]{GraphTerminologyExtended.png}
  \caption{Illustrated guide to the labeling terminology}
 \label{fig:term}
\end{figure}

@@

For the routing part of the algorithm, we work through the annotations $a \in A$ in the order they appear in the text, placing each as far up as possible, skipping any annotation that cannot be placed above its leader's source node. We will also use fixed ports located in the top left corner of each label. %This allows us to place annotations by only knowing their port location, which can be inferred from their leader's ending point.
The routing area, which is located between the text and label areas, will be used to bridge the gap between the highest reachable point within the routing graph and the highest possible label placement by connecting the two via an OPO-leader.%Kann man das so sagen?

The routing algorithm itself uses only the Graph $G$ and the set of sites $V_{ann} \subset V$ which will be routed using a depth-first search algorithm, restricted to only selecting vertices located above or to the right of the current vertex $v_{curr}$, prioritizing moving up whenever possible. It will terminate upon reaching the right text border or if all possible paths failed to reach the text border. At this point, it will return a set with routing information for each vertex, which contains a Path $P=\{v_1, \cdots, v_n\}$, leading from the site to the text area's border, along with information on how to draw the OPO-Segment that connects to the Label's port. If the routing for any given site failed, the path consists of a single vertex - the site. (For an illustration in Pseudocode see Alg.~\ref{alg:DFS}.)

@@

\DontPrintSemicolon
\KwData{A single annotation's source and its Graph}
\KwResult{A List of vertices describing the Leader's Path}

>>>>

\begin{figure}%{r}{0.35\textwidth}
 \captionsetup{justification=centering, margin=0.75cm}
 \centering
  \includegraphics[scale=0.95]{GraphTerminologyExtended.png}
  \caption{Illustrated guide to the labeling terminology}
 \label{fig:term}
\end{figure}

@@

For the routing part of the algorithm, we work through the annotations $a \in A$ in the order they appear in the text, placing each as far up as possible, skipping any annotation that cannot be placed in a reachable position above its leader's source. We will also use fixed ports located in the top left corner of each label. %This allows us to place annotations by only knowing their port location, which can be inferred from their leader's ending point.
The routing area, which is located between the text and label areas, will be used to bridge the gap between the highest currently reachable point within the routing graph and the highest possible label placement by connecting the two via an OPO-leader.%Kann man das so sagen?

The routing algorithm itself uses only the Graph $G$ and the set of sites $V_{ann} \subset V$ which will be routed using a depth-first search algorithm, using only vertices located above or to the right of the current vertex $v_{curr}$, prioritizing moving up whenever possible. It will terminate upon reaching the right text border or if all possible paths failed to reach the text border. At this point, it will return a set with routing information for each vertex, which contains a Path $P=\{v_1, \cdots, v_n\}$, leading from the site to the text area's border, along with information on how to draw the OPO-Segment that connects to the Label's port. If the routing for any given site failed, the path consists of a single vertex - the site. (For an illustration in Pseudocode see Alg.~\ref{alg:DFS}.)

@@

\DontPrintSemicolon
\KwData{A single annotation's source and its Graph}
\KwResult{A List of vertices describing the leader's path}
